Summary

### 2015-11-20 inst/examples/summary.Rmd
ok

Fraction of documents with entries for each annotation field.

@@

[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.tab)

>>>>

Fraction of documents with entries for each annotation field. For a full list of summaries for field contents, see [here](https://github.com/rOpenGov/fennica/tree/master/inst/examples/output.tables).

@@

[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)

[Discarded corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)
